\Large Clustering Vehicle Trips Identified from Automatic \\ Number Plate Recognition Camera Scans

### 2018-01-31 classification.tex
Added first results at the end - unformatted, just as a hack, will fix this later on

>>>>

\clearpage

\begin{table*}[t]
\centering
\begin{tabular}{rrrrrrr}
  \hline
 k & t300 & t450 & t600 & t900 & t1200 & t1800 \\
  \hline
1 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 \\
  2 & 543907.35 & 534453.24 & 534706.04 & 561666.18 & 618943.98 & 737557.49 \\
  3 & 822985.63 & 789214.80 & 760759.14 & 723082.06 & 719393.29 & 743001.88 \\
  4 & 913945.86 & 876675.37 & 838741.42 & 781306.76 & 754241.10 & 711478.70 \\
  5 & 1012979.13 & 943556.95 & 878417.35 & 786755.20 & 745483.33 & 683551.70 \\
  6 & 1084917.22 & 989249.70 & 905072.13 & 716272.22 & 730215.42 & 651959.66 \\
  7 & 1113954.86 & 1003744.40 & 852060.06 & 761738.57 & 713320.54 & 633101.34 \\
  8 & 1061923.12 & 972081.71 & 892493.94 & 776092.12 & 708701.00 & 606811.46 \\
   \hline
\end{tabular}
\caption{Calinski-Harabasz Criterion per k-cluster, per value of threshold}
\end{table*}

\begin{table}[!ht]
\centering
\begin{tabular}{rr}
  \hline
 threshold & best k \\
  \hline
t300 &   7 \\
  t450 &   7 \\
  t600 &   6 \\
  t900 &   5 \\
  t1200 &   4 \\
  t1800 &   3 \\
   \hline
\end{tabular}
\caption{Best k for each threshold}
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rr}
  \hline
 threshold & value \\
  \hline
t300 & 0.91 \\
  t450 & 0.90 \\
  t600 & 0.88 \\
  t900 & 0.84 \\
  t1200 & 0.79 \\
  t1800 & 0.71 \\
   \hline
\end{tabular}
\caption{$BetweenSS / TotalSS$ -- Amount of variance in data explained}
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 threshold & V1 & V2 & V3 & V4 & V5 & V6 & V7 \\
  \hline
t300 & 550 & 99091 & 7975 & 39032 & 2478 & 168677 & 338847 \\
  t450 & 666 & 10380 & 2948 & 45414 & 108877 & 163985 & 309736 \\
  t600 & 26568 & 865 & 97745 & 332060 & 171024 & 4408 &  \\
  t900 & 352029 & 74821 & 181295 & 11200 & 1787 &  &  \\
  t1200 & 189224 & 371318 & 49852 & 4593 &  &  &  \\
  t1800 & 26484 & 191957 & 388959 &  &  &  &  \\
   \hline
\end{tabular}
\caption{Sizes of each cluster for best k per threshold}
\end{table}

% latex table generated in R 3.3.1 by xtable 1.8-2 package
% Wed Jan 31 03:12:43 2018
\begin{table*}[ht]
\centering
\begin{tabular}{rrrrrrrrr}
  \hline
 & Trips & AvTrips & AvLength & AvDisOri & AvDisDes & AvFirstH & AvLastH & AvRest \\
  \hline
1 & 412.89 & 33.00 & 1.25 & 10.64 & 4.95 & 5.75 & 19.71 & 13.45 \\
  2 & 36.34 & 3.41 & 1.39 & 3.08 & 1.06 & 9.64 & 16.21 & 6.50 \\
  3 & 108.34 & 8.92 & 1.27 & 6.78 & 2.63 & 8.20 & 17.77 & 9.48 \\
  4 & 60.61 & 5.10 & 1.34 & 4.37 & 1.59 & 8.89 & 16.98 & 8.00 \\
  5 & 210.51 & 16.93 & 1.28 & 10.79 & 4.67 & 6.67 & 18.97 & 12.21 \\
  6 & 19.75 & 2.56 & 1.34 & 2.37 & 0.73 & 10.95 & 15.17 & 4.17 \\
  7 & 6.49 & 2.20 & 1.33 & 2.10 & 0.64 & 12.47 & 14.49 & 1.98 \\
   \hline
\end{tabular}
\caption{Centers for threshold = 300}
\end{table*}

% latex table generated in R 3.3.1 by xtable 1.8-2 package
% Wed Jan 31 03:12:43 2018
\begin{table*}[ht]
\centering
\begin{tabular}{rrrrrrrrr}
  \hline
 & Trips & AvTrips & AvLength & AvDisOri & AvDisDes & AvFirstH & AvLastH & AvRest \\  \hline
1 & 331.50 & 26.43 & 1.57 & 9.31 & 5.17 & 5.73 & 19.59 & 13.14 \\
  2 & 86.99 & 7.16 & 1.43 & 5.55 & 2.49 & 8.41 & 17.60 & 9.03 \\
  3 & 170.08 & 13.69 & 1.47 & 9.20 & 4.67 & 6.89 & 18.69 & 11.65 \\
  4 & 50.30 & 4.26 & 1.52 & 3.67 & 1.57 & 9.04 & 16.86 & 7.69 \\
  5 & 30.67 & 2.91 & 1.56 & 2.65 & 1.09 & 9.67 & 16.11 & 6.35 \\
  6 & 16.99 & 2.30 & 1.46 & 2.13 & 0.77 & 11.12 & 14.99 & 3.81 \\
  7 & 5.95 & 2.01 & 1.44 & 1.92 & 0.68 & 12.52 & 14.50 & 1.93 \\
   \hline
\end{tabular}
\caption{Centers for threshold = 450}
\end{table*}

% latex table generated in R 3.3.1 by xtable 1.8-2 package
% Wed Jan 31 03:12:43 2018
\begin{table*}[ht]
\centering
\begin{tabular}{rrrrrrrrr}
  \hline
 & Trips & AvTrips & AvLength & AvDisOri & AvDisDes & AvFirstH & AvLastH & AvRest \\
  \hline
1 & 60.90 & 5.04 & 1.58 & 4.13 & 1.95 & 8.78 & 17.20 & 8.24 \\
  2 & 271.76 & 21.64 & 1.79 & 8.77 & 5.37 & 5.72 & 19.42 & 12.80 \\
  3 & 34.38 & 3.07 & 1.68 & 2.76 & 1.27 & 9.38 & 16.41 & 6.90 \\
  4 & 6.39 & 1.92 & 1.52 & 1.83 & 0.69 & 12.45 & 14.51 & 1.99 \\
  5 & 18.96 & 2.28 & 1.57 & 2.11 & 0.85 & 10.74 & 15.24 & 4.41 \\
  6 & 131.86 & 10.66 & 1.61 & 7.53 & 4.09 & 7.32 & 18.27 & 10.74 \\
   \hline
\end{tabular}
\caption{Centers for threshold = 600}
\end{table*}

% latex table generated in R 3.3.1 by xtable 1.8-2 package
% Wed Jan 31 03:12:43 2018
\begin{table*}[ht]
\centering
\begin{tabular}{rrrrrrrrr}
  \hline
 & Trips & AvTrips & AvLength & AvDisOri & AvDisDes & AvFirstH & AvLastH & AvRest \\
  \hline
1 & 6.80 & 1.81 & 1.62 & 1.72 & 0.70 & 12.37 & 14.53 & 2.07 \\
  2 & 38.62 & 3.30 & 1.82 & 2.89 & 1.48 & 9.18 & 16.73 & 7.35 \\
  3 & 20.89 & 2.25 & 1.73 & 2.09 & 0.96 & 10.31 & 15.52 & 5.08 \\
  4 & 78.63 & 6.41 & 1.77 & 4.94 & 2.76 & 8.24 & 17.62 & 9.08 \\
  5 & 180.14 & 14.33 & 2.06 & 7.52 & 4.99 & 6.11 & 18.89 & 11.78 \\
   \hline
\end{tabular}
\caption{Centers for threshold = 900}
\end{table*}

% latex table generated in R 3.3.1 by xtable 1.8-2 package
% Wed Jan 31 03:12:43 2018
\begin{table*}[ht]
\centering
\begin{tabular}{rrrrrrrrr}
  \hline
 & Trips & AvTrips & AvLength & AvDisOri & AvDisDes & AvFirstH & AvLastH & AvRest \\
  \hline
1 & 22.82 & 2.29 & 1.84 & 2.11 & 1.06 & 10.00 & 15.76 & 5.60 \\
  2 & 7.19 & 1.76 & 1.68 & 1.68 & 0.71 & 12.30 & 14.55 & 2.14 \\
  3 & 44.85 & 3.73 & 1.90 & 3.16 & 1.73 & 8.98 & 17.02 & 7.76 \\
  4 & 114.34 & 9.12 & 2.30 & 5.92 & 3.98 & 6.93 & 18.21 & 10.43 \\
   \hline
\end{tabular}
\caption{Centers for threshold = 1200}
\end{table*}

% latex table generated in R 3.3.1 by xtable 1.8-2 package
% Wed Jan 31 03:12:43 2018
\begin{table*}[ht]
\centering
\begin{tabular}{rrrrrrrrr}
  \hline
 & Trips & AvTrips & AvLength & AvDisOri & AvDisDes & AvFirstH & AvLastH & AvRest \\
  \hline
1 & 54.75 & 4.42 & 2.33 & 3.52 & 2.21 & 8.45 & 17.40 & 8.35 \\
  2 & 24.54 & 2.31 & 1.98 & 2.13 & 1.15 & 9.72 & 16.00 & 6.06 \\
  3 & 7.52 & 1.69 & 1.77 & 1.61 & 0.72 & 12.23 & 14.58 & 2.22 \\
   \hline
\end{tabular}
\caption{Centers for threshold = 1800}
\end{table*}

\clearpage
